### 2019-07-19 wasp18.tex
WASP18 chapter more complete. Added Obs and Data Reduction chapter.

\begin{table}
\caption{Log of Observations}             
\label{log_table}      
\centering          
\begin{tabular}{cccccccc}
\hline\hline       
 Date & Epoch\footnotemark{a} & Telescope & Filter & Total exposures & Exposure time\footnotemark{b} & RMS\footnotemark{c} \\
 (UTC) &       &           &       &                   & (seconds) & (mmag)\\
\hline  
 2009 Oct 28 &-1904 & SMARTS 1 m & $I$ & 1412 & 1.5 & 8.49  \\
 2009 Oct 29 & -1903 & SMARTS 1 m & $I$ & 1435 & 2 & 5.67 \\
2009 Oct 30 & -1902 & SMARTS 1 m & $I$ & 1198 & 2  & 4.50 \\
 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
2016 Sep 24\footnotemark{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
2016 Sep 25\footnotemark{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
2016 Sep 26\footnotemark{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
2017 Sep 29\footnotemark{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
\hline                  
\end{tabular}
\footnotetext{a}{The epoch 0 is $T_{0}$ in Tables , for WASP-18b, WASP-19b and WASP-77Ab, respectively.}
\footnotetext{b}{For the variable exposure times, we consider the average during the night.}
\footnotetext{c}{The RMS values were computed from the best fitted model of each light curve.}
\footnotetext{d}{Light curves obtained with only one reference star.}
\end{table}

@@

>>>>

\begin{table*}
\caption{Log of Observations}             
\label{log_table}      
\centering          
\begin{tabular}{cccccccc}
\hline\hline       
 Date & Epoch\footnotemark{a} & Telescope & Filter & Total exposures & Exposure time\footnotemark{b} & RMS\footnotemark{c} \\
 (UTC) &       &           &       &                   & (seconds) & (mmag)\\
\hline  
 2009 Oct 28 &-1904 & SMARTS 1 m & $I$ & 1412 & 1.5 & 8.49  \\
 2009 Oct 29 & -1903 & SMARTS 1 m & $I$ & 1435 & 2 & 5.67 \\
2009 Oct 30 & -1902 & SMARTS 1 m & $I$ & 1198 & 2  & 4.50 \\
 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
2016 Sep 24\footnotemark{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
2016 Sep 25\footnotemark{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
2016 Sep 26\footnotemark{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
2017 Sep 29\footnotemark{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
\hline                  
\end{tabular}
\footnotetext{a}{The epoch 0 is $T_{0}$ in Tables , for WASP-18b, WASP-19b and WASP-77Ab, respectively.}
\footnotetext{b}{For the variable exposure times, we consider the average during the night.}
\footnotetext{c}{The RMS values were computed from the best fitted model of each light curve.}
\footnotetext{d}{Light curves obtained with only one reference star.}
\end{table*}

@@

\subsection{Limits on an additional perturber}

For the WASP-18b system we find a large region of instability when compared to the other two systems with the boundaries at the 1:2 interior
and 2:1 exterior mean-motion resonance. By over-plotting the RMS scatter of mid-transit times ($\rm TTV_{\rm RMS}$) for a certain value, we find
that the TTVs are relatively more sensitive at orbital architectures involving mean-motion resonances confirming the results by \citet{Agol2005} and \citet{Holman2005}. %This also applies to WASP-19 and WASP-77A.

As shown in Figure~\ref{megno_wasp18}, we find that a perturbing body of mass (upper limit) around $7-500~M_{\oplus}$ will produce an RMS of $83\,{\rm s}$ when located in the $P_2/P_1=$ 7:3, 5:2, 3:1, 17:5 and 4:1 exterior resonance. For the 1:3 interior resonance, a perturber mass (upper limit) as small as $1.9~M_{\oplus}$ could also cause a RMS mid-transit time scatter of $83\,{\rm s}$.

\begin{figure}
\includegraphics[width=1.0\columnwidth]{imagenes/WASP18_TraMos_83sec_Map001_GIMP_scaled.png}
\caption{MEGNO ($\langle Y \rangle$) stability map for the WASP-18 system. We over-plot the map with an upper mass of a hypothetical perturbing planet introducing a mid-transit time $\rm TTV_{\rm RMS}$ scatter of $83\,{\rm s}$ (solid line) as obtained in this study. The stipulated line is the upper mass limit as obtained from the RMS scatter $(30.9\, \rm m/s)$ of the radial-velocity curve. For initial conditions resulting in a quasi-periodic (i.e bounded) motion of the system, the $\langle Y\rangle$ value is close to 2.0 (color coded blue). For chaotic (i.e unstable) motion, the $\langle Y \rangle$ is diverging away from 2.0 (color coded red to yellow). Vertical arrows indicate $(P_2/P_1)$ orbital resonances between the perturbing body and the transiting planet. The two planets were assumed to be co-planar, and the perturbing planet's eccentricity was initially set to zero.
\emph{See electronic version for colors}.}
\label{megno_wasp18}
\end{figure}
